Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-08 prop_letter.tex
prop_letter.tex \section{Born} Updating...

Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
postulates of the quantum probability measures first, and then introduce
the Born rule which induces the quantum probability measures for each
state. When we shift our attention to QIVPMs, we also want to construct
a QIVPMs according to a simple rule. Since the ranges of the quantum
probability measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$,
respectively, if there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
to $\iota\left(x\right)\in\mathscr{I}$, then we can concatenate it
with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
and get a function~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
Although $\bar{\mu}$ has the same the domain and range, $\bar{\mu}$
may or may not be a QIVPM. For example, the following theorem highlight
the situation when $\bar{\mu}$ cannot be a QIVPM.

>>>>

Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
postulates of the quantum probability measures first, and then introduce
the Born rule which induces the quantum probability measures for each
state. When we shift our attention to QIVPMs, we also want to construct
a QIVPMs according to a simple rule. Since the ranges of the quantum
probability measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$,
respectively, if there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
to $\iota\left(x\right)\in\mathscr{I}$, then we can concatenate it
with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
and get a $\mathscr{I}$-valued function~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
Although $\bar{\mu}$ and QIVPMs have the same the domain and range,
$\bar{\mu}$ is not necessary a QIVPM. For example, the following
theorem highlight a situation where $\bar{\mu}$ cannot be a QIVPM.
